Visualizing Independence Using Extended Association Plots

### 2004-08-13 trunk/vcd/paper/JCGS.Rnw
*** empty log message ***
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@297 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(goals, gp = gp.max)
@
<<art-mosaic,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(art, gp = gp.max)
@
\caption{Extended mosaic plots for the Bundesliga and Arthritis data sets.}
\label{fig:assoc}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic2,fig=TRUE,echo=FALSE,height=6,width=8>>=
mygp.max <- function(x,y) gp.max(x, y, level = (1 - c(0.1, 0.01)/6))
tabplot(margin.table(ucb, c(2,1,3)), panel = function(x, ...) grid.mosaicplot(x, panel = TRUE, legend = FALSE, labels = FALSE, gp = mygp.max, space = 0.02, ...))
@
\caption{UCB admission with conditioned mosaic display.}
\label{fig:UCB-mosaic2}
\end{center}
\end{figure}

@@

\bibliography{vcd}

>>>>

\begin{figure}[htbp]
\begin{center}
<<haireye-Friendly,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(haireye, gp = gp.Friendly)
@
<<haireye-max,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(haireye, gp = gp.max)
@
\caption{Mosaic plots for the Hair-Eye-Color data.}
\label{fig:haireye}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
<<goals-Friendly,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(goals, gp = gp.Friendly)
@
<<goals-max,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(goals, gp = gp.max)
@
\caption{Mosaic plots for the Bundesliga data.}
\label{fig:goals}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
<<art-Friendly,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(art, gp = gp.Friendly)
@
<<art-max,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.mosaicplot(art, gp = gp.max)
@
\caption{Mosaic plots for the Arthritis data.}
\label{fig:art}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic2,fig=TRUE,echo=FALSE,height=6,width=8>>=
mygp.max <- function(x,y) gp.max(x, y, level = (1 - c(0.1, 0.01)/6))
tabplot(ucb, panel = function(x, ...) grid.mosaicplot(x, panel = TRUE, legend = FALSE, labels = FALSE, gp = mygp.max, space = 0.02, ...))
@
\caption{UCB admission with conditioned mosaic display.}
\label{fig:UCB-mosaic2}
\end{center}
\end{figure}

@@

\nocite{*}
\bibliography{vcd}
